pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-29 article.tex
Use another paragraph of @Giappo

An open question for each new diversification model is whether the increased
complexity is worth the extra computational resources \giovanni{I think here it is not only a matter of computational resources. I believe there two more factors: 1) developing a likelihood model takes time, human resources and therefore fundings; 2) in principle you can elaborate any model to be as complex as possibly requested, however there is a diminishing return on this. In fact the purpose of modelling for complex systems such as biology is to hypothesize the main driving factors of a process and trying to prove that they are indeed able to explain the main features of the phenomenon you want to explain. In my opinion the job of a modeller is to try to disentangle the intrinsic complexity of a system highlighting the main reasons of its behaviour. In such a light you don't want your model to be unnecessary complex.}. There are many
ways to answer this question. One possible experiment 
is to use a phylogeny of the new diversification model,
simulate its alignment and see how well our
current inference models are at retrieving the phylogeny.
If this difference is small enough, current models apparently
suffice.

>>>>

An open question for each new diversification model 
is whether the increased complexity is worth it. 
One of the purposes of modelling a complex systems
is to hypothesize the main driving factors of a process 
and trying to prove that they are indeed able 
to explain the main features of the phenomenon you want to explain.
Due to this, there are diminishing returns on adding complexity
to a model: the job of a modeller is to try to 
disentangle the intrinsic complexity of a system 
highlighting the main reasons of its behaviour. 
In such a light you don't want your model to be unnecessary complex.
Additionally, developing a likelihood model takes time, 
human resources, fundings and can strain computational resources.

When assuming that a new diversification model is worth the
(philosophical) effort, there are many ways to measure
if the new model indeed gives a better explanation. 
One possible experiment 
is to use a phylogeny of the new diversification model,
simulate its alignment and see how well our
current inference models are at retrieving the phylogeny.
If this difference is small enough, current models apparently
suffice.
